---
title: "Regression"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r, include=FALSE}
# Note: Need to read in the data with `tidyverse` as that is the only way to make it availabe when knitting R markdown to HTML
library(tidyverse)
zillow_oc_2017 <- read_csv(file="../../02-Evr_Read_CSV/Resources/zillow_orange_county_2017.csv")
```

### Generte a simple linear regression

```{r}
lm(homevalue ~ finishedsquarefeet,zillow_oc_2017)
```

### Show detailed results of a linear regression model

```{r}
summary(lm(homevalue ~ finishedsquarefeet,zillow_oc_2017))
```

### Store the results from the linear regression model

```{r}
model <- lm(homevalue ~ finishedsquarefeet,zillow_oc_2017)
```

### Calculate the home values for y

```{r}
yvals <- model$coefficients['finishedsquarefeet']*zillow_oc_2017$finishedsquarefeet + model$coefficients['(Intercept)']
```

### Create a scatter plot of the finished square feet by homevalue

```{r}
plt <- ggplot(zillow_oc_2017,aes(x=finishedsquarefeet,y=homevalue))
```

### Generate the scatter plot with a line representing the linear model

```{r}
plt + geom_point() + geom_line(aes(y=yvals), color = "red")
```

### Show detailed results of a multiple linear regression model

```{r}
summary(lm(homevalue ~ finishedsquarefeet + bedroomcnt + bathroomcnt + lotsizesquarefeet + poolcnt + yearbuilt + taxvaluedollarcnt,zillow_oc_2017))
```